---
title: "ICAR Items"
output: 
  html_document:
    toc: TRUE
    toc_float: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, 
                      message = FALSE, 
                      warning = FALSE,
                      results = 'asis')
```

# Description

ICAR is an acronym for International Cognitive Ability Resource. This file provides a listing of the item labels for the various ICAR items sorted by type. The content needed to administer these items is intentionally excluded here. To access these items, researchers must register at the [ICAR-Project website](https://icar-project.com/). The items are available in the public-domain but they can only be accessed after registration.


# Table

```{r}
library(rio)
library(tidyverse)
library(DT)

did4 = import("DID24jun2019.xlsx", sheet = 4, skip = 5) %>%
  select(-starts_with("..")) %>%
  select(-starts_with("SEE"))

did4 %>%
  datatable(
    colnames = c("Item ID",
                 "Number",
                 "Item",
                 "Scale", 
                 "Response Type",
                 "Unique"),
    filter = "top", rownames = F)
```

